---
title: "MCMC_CSG"
author: "Kristen Tuosto"
date: "2023-04-01"
output: html_document
---

```{r read in df & libraries}
#load libraries
library(dplyr)
library(ggplot2)
library(tidyr)
#library(AICcmodavg)
library(MCMCglmm)

#read in df 

df <- read.csv("C:/Users/ktuos/Desktop/ABRP Excel Files/R Codes/Genetic_Master_June_7_2023.csv")

pedigree <- read.csv("C:/Users/ktuos/Desktop/ABRP Excel Files/R Codes/pedigree_df_v4.csv")

df$Sex <- as.factor(df$Sex)

df <- df %>% drop_na(Age)


```

```{r filter df by bone}


df <- df %>% drop_na(FDML.BM.kg)

#Humerus
humerus <- filter(df, Bone.Code == "Humerus")

# Remove blanks
humerus <- humerus[humerus$animal != "", ]

humerus <- humerus %>% drop_na(DIL)

#write.csv(humerus, "C:/Users/ktuos/Desktop/ABRP Excel Files/humerus_only.csv", row.names=FALSE)

#Radius
radius <- filter(df, Bone.Code == "Radius")

# Remove blanks
radius <- radius[radius$animal != "", ]

radius <- radius %>% drop_na(DIL)

#Femur
femur <- filter(df, Bone.Code == "Femur")

# Remove blanks
femur <- femur[femur$animal != "", ]

femur <- femur %>% drop_na(DIL)

#Tibia
tibia <- filter(df, Bone.Code == "Tibia")

# Remove blanks
tibia <- tibia[tibia$animal != "", ]

tibia <- tibia %>% drop_na(DIL)

```

```{r ordering df}

library(MasterBayes)


# Sort the pedigree data
ordered_pedigree <- orderPed(pedigree)

# Continue with your analysis using the ordered pedigree

str(ordered_pedigree)

#write.csv(ordered_pedigree, "C:/Users/ktuos/Desktop/ABRP Excel Files/ordered_pedigree.csv", row.names=FALSE)

```

# Defining Priors
```{r animal mode setup}

#inverse relatedness matrix
Ainv <- inverseA(ordered_pedigree)$Ainv # Relatedness matrix does not need to be in the same df as data

# Defining priors and the residual variance
prior1.1 <- list(
  G = list(G1 = list(V = 1, nu = 0.002)),
  R = list(V = 1, nu = 0.002)
)

# Defining priors and the residual variance
prior1.1.2 <- list(
  G = list(G1 = list(V = 1, nu = 0.05)),
  R = list(V = 1, nu = 0.05)
)

```

#Functions
###%CA function
```{r %CA function}
#Area function where we can change the response variable and the predictor variable, therefor this function can be used to test rank and rainfall variables. 

PCA_mcmc <- function(df, pred_vars) {
  res_formula <- as.formula(paste("P.CA ~ Age + Sex +", paste(pred_vars, collapse = " + ")))

  model <- MCMCglmm(res_formula,
                    random = ~ animal, 
                    ginv = list(animal = Ainv),
                    prior = prior1.1.2,
                    data = df,
                    nitt = 500000, 
                    thin = 50, 
                    burnin = 55500, 
                    verbose = FALSE)
  
  print(autocorr.diag(model$VCV))
  print(autocorr.diag(model$Sol))
  plot(model$VCV)
  return(summary(model))
}


# Usage/Setup, note the predictor variable is in " " 
# PCA_mcmc(humerus, "GPRank")

```

###Area function
```{r area function}
area_mcmc_multiple <- function(df, res_vars, pred_var_name) {
  summaries <- list()
  
  for (i in seq_along(res_vars)) {
    res_var_name <- res_vars[i]
    pred_var <- df[[pred_var_name]]
    
    res_formula <- as.formula(paste("log(", res_var_name, ") ~ log(FDML.BM.kg) + Sex +", pred_var_name))
    
    model <- MCMCglmm(res_formula,
                      random = ~ animal, 
                      ginv = list(animal = Ainv),
                      prior = prior1.1.2,
                      data = df,
                      nitt = 500000, 
                      thin = 50, 
                      burnin = 55500, 
                      verbose = FALSE)
    
    summaries[[i]] <- summary(model)
    plot(model$VCV)
    print(autocorr.diag(model$VCV))
  }
  
  return(summaries)
}

```

###2nd moment of area function
```{r 2nd Moment of area function}
moment2nd_mcmc_multiple <- function(df, res_vars, pred_var_name) {
  summaries <- list()
  
  for (i in seq_along(res_vars)) {
    res_var_name <- res_vars[i]
    pred_var <- df[[pred_var_name]]
    
    res_formula <- as.formula(paste("log(", res_var_name, ") ~ log(FDML.BM.kg*MXL^2) + Sex +", pred_var_name))
    
    model <- MCMCglmm(res_formula,
                      random = ~ animal, 
                      ginv = list(animal = Ainv),
                      prior = prior1.1.2,
                      data = df,
                      nitt = 500000, 
                      thin = 50, 
                      burnin = 55500, 
                      verbose = FALSE)
    
    summaries[[i]] <- summary(model)
    plot(model$VCV)
    print(autocorr.diag(model$VCV))
  }
  
  return(summaries)
}
```

###Section moduli function
```{r section moduli function}

moduli_mcmc_multiple <- function(df, res_vars, pred_var_name) {
  summaries <- list()
  
  for (i in seq_along(res_vars)) {
    res_var_name <- res_vars[i]
    pred_var <- df[[pred_var_name]]
    
    res_formula <- as.formula(paste("log(", res_var_name, ") ~ log(FDML.BM.kg*MXL) + Sex +", pred_var_name))
    
    model <- MCMCglmm(res_formula,
                      random = ~ animal, 
                      ginv = list(animal = Ainv),
                      prior = prior1.1.2,
                      data = df,
                      nitt = 500000, 
                      thin = 50, 
                      burnin = 55500, 
                      verbose = FALSE)
    
    summaries[[i]] <- summary(model)
    plot(model$VCV)
    print(autocorr.diag(model$VCV))
  }
  
  return(summaries)
}
```

###CI plot
```{r CI plot function}
plot.estimates <- function(x) {
  if (class(x) != "summary.mcmc")
    x <- summary(x)
  n <- dim(x$statistics)[1]
  par(mar=c(2, 7, 4, 1))
  plot(x$statistics[,1], n:1,
       yaxt="n", ylab="",
       xlim=range(x$quantiles)*1.2,
       pch=19,
       main="Posterior means and 95% credible intervals")
  grid()
  axis(2, at=n:1, rownames(x$statistics), las=2)
  arrows(x$quantiles[,1], n:1, x$quantiles[,5], n:1, code=0)
  abline(v=0, lty=2)
}
```

###Autocorralation plots
```{r autocorralation plot function} 
plot.acfs <- function(x) {
  n <- dim(x)[2]
  par(mfrow=c(ceiling(n/2),2), mar=c(3,2,3,0))
  for (i in 1:n) {
    acf(x[,i], lag.max=100, main=colnames(x)[i])
    grid()
  }
}

```

###MCMC malleable model function
```{r MCMC}
run_mcmc_analysis <- function(response_var_tansformation, rain_var, rank_var, fdml_transformation, data, df_name, prior, 
                              nitt = 500000, thin = 50, burnin = 55500, verbose = FALSE) {
  
  # Run MCMCglmm model
  model_result <- MCMCglmm(as.formula(paste0(response_var_tansformation, " ~ ", fdml_transformation, " + Sex + ", 
                           rain_var, " + ", rank_var)),
                           random = ~ animal, 
                           ginv = list(animal = Ainv),
                           prior = prior,
                           data = data,
                           nitt = nitt, 
                           thin = thin, 
                           burnin = burnin, 
                           verbose = verbose)
  
  # Plot the solutions and save to PDF
  pdf(paste0(df_name, "_", response_var_tansformation, "_", rain_var, "_", rank_var, "_plot.pdf"))
  plot(model_result$Sol)
  dev.off()

  
  # Plot the variance components
  plot(model_result$VCV)
  
  # Print summary and save to text file
  sink(paste0(df_name, "_", response_var_tansformation, "_", rain_var, "_", rank_var, ".txt"))
  print(summary(model_result))
  sink()
  
  # Return the model result and other diagnostics
  list(
    model = model_result,
    effective_size_sol = effectiveSize(model_result[["Sol"]]),
    effective_size_vcv = effectiveSize(model_result[["VCV"]])
  )
  print(summary(model_result))
  return(model_result)
}

```

###Diagnostic function
```{r diagnostic}
run_diagnostics <- function(model_result) {
  
  # Heidelberg stationarity test
  heidel_vcv <- heidel.diag(model_result[["VCV"]])
  heidel_sol <- heidel.diag(model_result[["Sol"]])
  
  raftery_res <- raftery.diag(model_result, q=0.025, r=0.005, s=0.95, converge.eps=0.001)
  
  # Geweke diagnostics
  geweke_sol_diag <- geweke.diag(model_result$Sol)
  geweke_sol_plot <- geweke.plot(model_result$Sol)
  
  geweke_vcv_diag <- geweke.diag(model_result$VCV)
  geweke_vcv_plot <- geweke.plot(model_result$VCV)
  
  # Autocorrelation diagnostics
  acf_sol_plot <- plot.acfs(model_result$Sol)
  acf_vcv_plot <- plot.acfs(model_result$VCV)
  
  autocorr_vcv_diag <- autocorr.diag(model_result$VCV)
  autocorr_sol_diag <- autocorr.diag(model_result$Sol)
  
  # CI plots
  ci_sol_plot <- plot.estimates(model_result$Sol)
  ci_vcv_plot <- plot.estimates(model_result$VCV)
  
  # Return results in a list for further analysis
  list(
    heidel_vcv = heidel_vcv,
    heidel_sol = heidel_sol,
    raftery = raftery_res,
    geweke_sol_diag = geweke_sol_diag,
    geweke_sol_plot = geweke_sol_plot,
    geweke_vcv_diag = geweke_vcv_diag,
    geweke_vcv_plot = geweke_vcv_plot,
    acf_sol_plot = acf_sol_plot,
    acf_vcv_plot = acf_vcv_plot,
    autocorr_vcv_diag = autocorr_vcv_diag,
    autocorr_sol_diag = autocorr_sol_diag,
    ci_sol_plot = ci_sol_plot,
    ci_vcv_plot = ci_vcv_plot
  )
}

# Example of how to use the function
# diagnostic_results_test <- run_diagnostics(model_test)
# 
# diagnostic_results_test
```

###Heritability function
```{r heritability}
compute_posterior_heritability <- function(model_result) {
  
  # Compute posterior mode of the variance components
  vcv_mode <- posterior.mode(model_result$VCV)
  
  # Calculate 95% HPD interval for the variance components
  vcv_hpd <- HPDinterval(model_result$VCV)
  
  # Calculate heritability based on the posterior distributions of the animal and units variance components
  heritability_posterior <- model_result$VCV[, "animal"] / 
                            (model_result$VCV[, "animal"] + model_result$VCV[, "units"])
  
  # Compute posterior mode of heritability
  heritability_mode <- posterior.mode(heritability_posterior)
  print(heritability_mode)
  
  # Calculate 95% HPD interval for heritability
  heritability_hpd <- HPDinterval(heritability_posterior, 0.95)
  print(heritability_hpd)
  
  # Plot the posterior distribution of heritability
  plot(heritability_posterior, main = "Posterior Distribution of Heritability")
  
  # Return results in a list for further analysis
  list(
    vcv_mode = vcv_mode,
    vcv_hpd = vcv_hpd,
    heritability_posterior = heritability_posterior,
    heritability_mode = heritability_mode,
    heritability_hpd = heritability_hpd
  )
}

# Example of how to use the function
# heritability_results <- compute_posterior_heritability(model_test)

```

###Run and diagnostic MCMC function
```{r r-hat test}
run_and_diagnose_mcmc <- function(response_var_transformation, rain_var, rank_var, fdml_transformation, 
                                  num_runs = 5, prior, data) {
  library(coda)
  
  # Run MCMC model multiple times
  fits <- list()
  for (i in 1:num_runs) {
    formula_str <- paste0(response_var_transformation," ~ ", fdml_transformation, " + ", 
                          rain_var, " + ", rank_var, " + Sex")
    fits[[i]] <- MCMCglmm(as.formula(formula_str),
                          random = ~ animal, 
                          ginv = list(animal = Ainv),
                          prior = prior,
                          data = data,
                          nitt = 500000, 
                          thin = 50, 
                          burnin = 25500, 
                          verbose = FALSE)
  }
  
   # Pool solutions and VCVs
  mcmc_list_Sol <- mcmc.list(lapply(fits, function(x) x$Sol))
  mcmc_list_VCV <- mcmc.list(lapply(fits, function(x) x$VCV))
  
  # Gelman-Rubin diagnostic plots and diagnostics
  gelman.plot(mcmc_list_Sol)
  sol_diag <- gelman.diag(mcmc_list_Sol)
  print(sol_diag)
  
  gelman.plot(mcmc_list_VCV)
  vcv_diag <- gelman.diag(mcmc_list_VCV)
  print(vcv_diag)
  
  # Trace plots
  par(mfrow = c(8, 2), mar = c(2, 1, 1, 1))
  plot(mcmc_list_Sol, ask = F, auto.layout = F)
  
  par(mfrow = c(8, 2), mar = c(2, 1, 1, 1))
  plot(mcmc_list_VCV, ask = F, auto.layout = F)
  
  # Return the diagnostics for further analysis
  list(
    sol_diag = sol_diag,
    vcv_diag = vcv_diag
  )
}

```

###Posterior predictive check function
```{r post pred check}

posterior_predictive_check <- function(model, data_name, response_var, log_transform = FALSE) {
  
  # Number of simulations
  nsimulations <- 100
  sims <- vector("list", nsimulations)
  
  # Simulating data from the model
  for (i in 1:nsimulations) {
    sims[[i]] <- simulate(model)
  }
  
  # Extracting observed data and applying log transformation if needed
  observed_data <- if(log_transform) log(get(data_name)[[response_var]]) else get(data_name)[[response_var]]
  
  # Calculating observed statistics
  observed_min <- min(observed_data)
  observed_max <- max(observed_data)
  observed_mean <- mean(observed_data)
  
  # Calculating statistics from simulated data
  simulated_mins <- sapply(sims, min)
  simulated_maxs <- sapply(sims, max)
  simulated_means <- sapply(sims, mean)
  
  # Plotting histograms
  hist(observed_data, freq=FALSE, main="Posterior Predictive Check", xlab=response_var, col=rgb(0.2,0.8,0.5,1))
  for (i in 1:length(sims)) {
    hist(sims[[i]], freq=FALSE, col=rgb(0.8,0.2,0.5,0.01), add=TRUE)
  }
  
  # Comparing means
  hist(simulated_means, main="Distribution of Simulated Means", xlab=paste0("Mean ", response_var))
  abline(v=observed_mean, col="red")
  
  # Comparing observed and predicted values
  predicted_values <- predict(model)
  plot(observed_data, predicted_values)
  abline(0, 1, col = "red")  # line of equality for reference
}

```

```{r}
check_all_parameters_normality <- function(bayesian_model) {
  
  # Get all parameter names
  parameter_names <- colnames(bayesian_model$Sol)
  results <- list()
  
  # Loop through each parameter and check its normality
  for (parameter in parameter_names) {
    samples <- bayesian_model$Sol[, parameter]
    
    # Display QQ-plot for each parameter
    qqnorm(samples, main = paste("QQ-plot for", parameter))
    qqline(samples, col = "red")
    
    # Append Shapiro-Wilk test results to the results list
    results[[parameter]] <- shapiro.test(samples)
  }
  
  # Return results for all parameters
  return(results)
}

```


#Checking normality function
```{r normality test}
check_normality <- function(model, data, response_var) {
  
  # Predicting values using the model
  predicted_values <- predict(model)
  
  # Extracting observed data
  observed_data <- data[[response_var]]
  
  # Calculating residuals
  residuals <- observed_data - predicted_values
  
  # Display QQ-plot
  qqnorm(residuals)
  qqline(residuals)
  
  # Return result of Shapiro-Wilk test
  return(shapiro.test(residuals))
}

```


#Humerus
##Gestation
###%CA
####Rank & Rainfall
```{r}
h_GPR_PCA <- PCA_mcmc(humerus, "GPRank")

h_GPR_PCA

h_MRC_PCA <- PCA_mcmc(humerus, "MRC")

h_MRC_PCA

h_GPDD_PCA <- PCA_mcmc(humerus, "prop_droughtdays")

h_GPDD_PCA

h_GR_PCA <- PCA_mcmc(humerus, "gest_rain")

h_GR_PCA
```

Not good results for %CA...discuss with Chris on what can and cannot be done with this variable 

###Area measurements 
####Rank
```{r area}

# Define response variables and corresponding predictor variable
area_response_vars <- c("TA", "MA", "CA")
GPR_predictor_var <- "GPRank"
MRC_predictor_var <- "MRC"

# Call the function
h_GPR_area_result_summaries <- area_mcmc_multiple(humerus, area_response_vars, GPR_predictor_var)

h_GPR_area_result_summaries

# Call the function
h_MRC_area_result_summaries <- area_mcmc_multiple(humerus, area_response_vars, MRC_predictor_var)

h_MRC_area_result_summaries
```

####Rain
```{r area}

# Define your response variables and corresponding predictor variable
area_response_vars <- c("TA", "MA", "CA")
GPDD_predictor_var <- "prop_droughtdays"
GR_predictor_var <- "gest_rain"

# Call the function
h_GPDD_area_result_summaries <- area_mcmc_multiple(humerus, area_response_vars, GPDD_predictor_var)

# Call the function
h_GR_area_result_summaries <- area_mcmc_multiple(humerus, area_response_vars, GR_predictor_var)

h_GR_area_result_summaries

```

###Moment of area measurements
####Rank
```{r I & J}

# Define your response variables and corresponding predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
GPR_predictor_var <- "GPRank"
MRC_predictor_var <- "MRC"

# Call the function
h_GPR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(humerus, moment2nd_response_vars, GPR_predictor_var)

h_GPR_2ndmoment_result_summaries

# Call the function
h_MRC_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(humerus, moment2nd_response_vars, MRC_predictor_var)

h_MRC_2ndmoment_result_summaries
```

####Rain
```{r I & J}

# Define your response variables and corresponding predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
GPDD_predictor_var <- "prop_droughtdays"
GR_predictor_var <- "gest_rain"

# Call the function
h_GPDD_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(humerus, moment2nd_response_vars, GPDD_predictor_var)

h_GPDD_2ndmoment_result_summaries

# Call the function
h_GR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(humerus, moment2nd_response_vars, GR_predictor_var)

h_GR_2ndmoment_result_summaries
```

###section moduli
####Rank
```{r Z}

# Define your response variables and corresponding predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
GPR_predictor_var <- "GPRank"
MRC_predictor_var <- "MRC"

# Call the function
h_GPR_moduli_result_summaries <- moduli_mcmc_multiple(humerus, moduli_response_vars, GPR_predictor_var)

h_GPR_moduli_result_summaries

# Call the function
h_MRC_moduli_result_summaries <- moduli_mcmc_multiple(humerus, moduli_response_vars, MRC_predictor_var)

h_MRC_moduli_result_summaries
```

####Rain
```{r Z}

# Define your response variables and corresponding predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
GPDD_predictor_var <- "prop_droughtdays"
GR_predictor_var <- "gest_rain"

# Call the function
h_GPDD_moduli_result_summaries <- moduli_mcmc_multiple(humerus, moduli_response_vars, GPDD_predictor_var)

h_GPDD_moduli_result_summaries

# Call the function
h_GR_moduli_result_summaries <- moduli_mcmc_multiple(humerus, moduli_response_vars, GR_predictor_var)

h_GR_moduli_result_summaries
```

##DIC Table Humerus
```{r DIC table rank & rain gestation}

dic_table_rank_h <- data.frame(
  Bone = c("%Ca", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)



# Retrieve and store the DIC values for each model and bone
dic_table_rank_h$Model1 <- c(unlist(h_GPR_PCA$DIC),
                      unlist(h_GPR_area_result_summaries[[1]]$DIC),
                      unlist(h_GPR_area_result_summaries[[2]]$DIC),
                      unlist(h_GPR_area_result_summaries[[3]]$DIC),
                      unlist(h_GPR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(h_GPR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(h_GPR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(h_GPR_moduli_result_summaries[[1]]$DIC),
                      unlist(h_GPR_moduli_result_summaries[[2]]$DIC),
                      unlist(h_GPR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rank_h$Model2 <- c(unlist(h_MRC_PCA$DIC),
                      unlist(h_MRC_area_result_summaries[[1]]$DIC),
                      unlist(h_MRC_area_result_summaries[[2]]$DIC),
                      unlist(h_MRC_area_result_summaries[[3]]$DIC),
                      unlist(h_MRC_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(h_MRC_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(h_MRC_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(h_MRC_moduli_result_summaries[[1]]$DIC),
                      unlist(h_MRC_moduli_result_summaries[[2]]$DIC),
                      unlist(h_MRC_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rank_h) <- c("Geometric Properties", "Proportional Rank", "Ordinal Rank")


# Add a new column indicating which predictor variable is lower
dic_table_rank_h$Lower_Predictor <- ifelse(
  dic_table_rank_h$`Proportional Rank` < dic_table_rank_h$`Ordinal Rank`,
  "Proportion Rank", "Ordinal Rank"
)

print(dic_table_rank_h)


#write.csv(dic_table_rank_h, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rank_gest_h_CSG.csv", row.names=FALSE)

dic_table_rain_h <- data.frame(
  Bone = c("%Ca", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)



# Retrieve and store the DIC values for each model and bone
dic_table_rain_h$Model1 <- c(unlist(h_GR_PCA$DIC),
                      unlist(h_GR_area_result_summaries[[1]]$DIC),
                      unlist(h_GR_area_result_summaries[[2]]$DIC),
                      unlist(h_GR_area_result_summaries[[3]]$DIC),
                      unlist(h_GR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(h_GR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(h_GR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(h_GR_moduli_result_summaries[[1]]$DIC),
                      unlist(h_GR_moduli_result_summaries[[2]]$DIC),
                      unlist(h_GR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rain_h$Model2 <- c(unlist(h_GPDD_PCA$DIC),
                      unlist(h_GPDD_area_result_summaries[[1]]$DIC),
                      unlist(h_GPDD_area_result_summaries[[2]]$DIC),
                      unlist(h_GPDD_area_result_summaries[[3]]$DIC),
                      unlist(h_GPDD_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(h_GPDD_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(h_GPDD_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(h_GPDD_moduli_result_summaries[[1]]$DIC),
                      unlist(h_GPDD_moduli_result_summaries[[2]]$DIC),
                      unlist(h_GPDD_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rain_h) <- c("Geometric Properties", "Cumulative Rainfall", "Proportion of Drought Days")

# Add a new column indicating which predictor variable is lower
dic_table_rain_h$Lower_Predictor <- ifelse(
  dic_table_rain_h$`Cumulative Rainfall` < dic_table_rain_h$`Proportion of Drought Days`,
  "Cumulative Rainfall", "Proportion of Drought Days"
)

#write.csv(dic_table_rain_h, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rain_gest_h_CSG.csv", row.names=FALSE)

print(dic_table_rain_h)
```


#Year 1

```{r year 1 subset}

humerus_1 <- subset(humerus, Age > .6)

```

#Humerus
##%CA
####Rank & Rainfall
```{r}
h_BPR_PCA <- PCA_mcmc(humerus_1, "BPRank") 

h_BPR_PCA

h_MRB_PCA <- PCA_mcmc(humerus_1, "MRB")

h_MRB_PCA

h_BPDD_PCA <- PCA_mcmc(humerus_1, "prop_droughtdays_1year")

h_BPDD_PCA

h_BR_PCA <- PCA_mcmc(humerus_1, "one_year_rain")

h_BR_PCA
```

Not good results for %CA...discuss with Chris on what can and cannot be done with this variable 

###Area measurements 
####Rank
```{r area}

# Define your response variables and correspondinB predictor variable
area_response_vars <- c("TA", "MA", "CA")
BPR_predictor_var <- "BPRank"
MRB_predictor_var <- "MRB"

# Call the function
h_BPR_area_result_summaries <- area_mcmc_multiple(humerus_1, area_response_vars, BPR_predictor_var)

h_BPR_area_result_summaries

# Call the function
h_MRB_area_result_summaries <- area_mcmc_multiple(humerus_1, area_response_vars, MRB_predictor_var)

h_MRB_area_result_summaries
```

####Rain
```{r area}

# Define your response variables and correspondinB predictor variable
area_response_vars <- c("TA", "MA", "CA")
BPDD_predictor_var <- "prop_droughtdays_1year"
BR_predictor_var <- "one_year_rain"

# Call the function
h_BPDD_area_result_summaries <- area_mcmc_multiple(humerus_1, area_response_vars, BPDD_predictor_var)

# Call the function
h_BR_area_result_summaries <- area_mcmc_multiple(humerus_1, area_response_vars, BR_predictor_var)

h_BR_area_result_summaries

```

##Moment of area measurements
####Rank
```{r I & J}

# Define your response variables and corresponding predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
BPR_predictor_var <- "BPRank"
MRB_predictor_var <- "MRB"

# Call the function
h_BPR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(humerus_1, moment2nd_response_vars, BPR_predictor_var)

h_BPR_2ndmoment_result_summaries

# Call the function
h_MRB_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(humerus_1, moment2nd_response_vars, MRB_predictor_var)

h_MRB_2ndmoment_result_summaries
```

####Rain
```{r I & J}

# Define your response variables and correspondinB predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
BPDD_predictor_var <- "prop_droughtdays_1year"
BR_predictor_var <- "one_year_rain"

# Call the function
h_BPDD_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(humerus_1, moment2nd_response_vars, BPDD_predictor_var)

h_BPDD_2ndmoment_result_summaries

# Call the function
h_BR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(humerus_1, moment2nd_response_vars, BR_predictor_var)

h_BR_2ndmoment_result_summaries
```

##section moduli
####Rank
```{r Z}

# Define your response variables and correspondinB predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
BPR_predictor_var <- "BPRank"
MRB_predictor_var <- "MRB"

# Call the function
h_BPR_moduli_result_summaries <- moduli_mcmc_multiple(humerus_1, moduli_response_vars, BPR_predictor_var)

h_BPR_moduli_result_summaries

# Call the function
h_MRB_moduli_result_summaries <- moduli_mcmc_multiple(humerus_1, moduli_response_vars, MRB_predictor_var)

h_MRB_moduli_result_summaries
```

####Rain
```{r Z}

# Define your response variables and correspondinB predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
BPDD_predictor_var <- "prop_droughtdays_1year"
BR_predictor_var <- "one_year_rain"

# Call the function
h_BPDD_moduli_result_summaries <- moduli_mcmc_multiple(humerus_1, moduli_response_vars, BPDD_predictor_var)

h_BPDD_moduli_result_summaries

# Call the function
h_BR_moduli_result_summaries <- moduli_mcmc_multiple(humerus_1, moduli_response_vars, BR_predictor_var)

h_BR_moduli_result_summaries
```

##DIC Table humerus_1
```{r DIC table rank & rain Year 1}

dic_table_rank_1 <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)

# Retrieve and store the DIC values for each model and bone
dic_table_rank_1$Model1 <- c(unlist(h_BPR_PCA$DIC),
                      unlist(h_BPR_area_result_summaries[[1]]$DIC),
                      unlist(h_BPR_area_result_summaries[[2]]$DIC),
                      unlist(h_BPR_area_result_summaries[[3]]$DIC),
                      unlist(h_BPR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(h_BPR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(h_BPR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(h_BPR_moduli_result_summaries[[1]]$DIC),
                      unlist(h_BPR_moduli_result_summaries[[2]]$DIC),
                      unlist(h_BPR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rank_1$Model2 <- c(unlist(h_MRB_PCA$DIC),
                      unlist(h_MRB_area_result_summaries[[1]]$DIC),
                      unlist(h_MRB_area_result_summaries[[2]]$DIC),
                      unlist(h_MRB_area_result_summaries[[3]]$DIC),
                      unlist(h_MRB_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(h_MRB_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(h_MRB_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(h_MRB_moduli_result_summaries[[1]]$DIC),
                      unlist(h_MRB_moduli_result_summaries[[2]]$DIC),
                      unlist(h_MRB_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rank_1) <- c("Geometric Properties", "Proportional Rank", "Ordinal Rank")

# Add a new column indicatinB which predictor variable is lower
dic_table_rank_1$Lower_Predictor <- ifelse(
  dic_table_rank_1$`Proportional Rank` < dic_table_rank_1$`Ordinal Rank`,
  "Proportion Rank", "Ordinal Rank"
)

print(dic_table_rank_1)


#write.csv(dic_table_rank_1, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rank_radius1_CSG.csv", row.names=FALSE)

dic_table_rain_1 <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)

# Retrieve and store the DIC values for each model and bone
dic_table_rain_1$Model1 <- c(unlist(h_BR_PCA$DIC),
                      unlist(h_BR_area_result_summaries[[1]]$DIC),
                      unlist(h_BR_area_result_summaries[[2]]$DIC),
                      unlist(h_BR_area_result_summaries[[3]]$DIC),
                      unlist(h_BR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(h_BR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(h_BR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(h_BR_moduli_result_summaries[[1]]$DIC),
                      unlist(h_BR_moduli_result_summaries[[2]]$DIC),
                      unlist(h_BR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rain_1$Model2 <- c(unlist(h_BPDD_PCA$DIC),
                      unlist(h_BPDD_area_result_summaries[[1]]$DIC),
                      unlist(h_BPDD_area_result_summaries[[2]]$DIC),
                      unlist(h_BPDD_area_result_summaries[[3]]$DIC),
                      unlist(h_BPDD_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(h_BPDD_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(h_BPDD_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(h_BPDD_moduli_result_summaries[[1]]$DIC),
                      unlist(h_BPDD_moduli_result_summaries[[2]]$DIC),
                      unlist(h_BPDD_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rain_1) <- c("Geometric Properties", "Cumulative Rainfall", "Proportion of Drought Days")

# Add a new column indicatinB which predictor variable is lower
dic_table_rain_1$Lower_Predictor <- ifelse(
  dic_table_rain_1$`Cumulative Rainfall` < dic_table_rain_1$`Proportion of Drought Days`,
  "Cumulative Rainfall", "Proportion of Drought Days"
)

print(dic_table_rain_1) 

#write.csv(dic_table_rain_1, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rain_radius1_CSG.csv", row.names=FALSE)

```


#radius
##Gestation
###%CA
####Rank & Rainfall
```{r}
r_GPR_PCA <- PCA_mcmc(radius, "GPRank")

r_GPR_PCA

r_MRC_PCA <- PCA_mcmc(radius, "MRC")

r_MRC_PCA

r_GPDD_PCA <- PCA_mcmc(radius, "prop_droughtdays")

r_GPDD_PCA

r_GR_PCA <- PCA_mcmc(radius, "gest_rain")

r_GR_PCA
```

Not good results for %CA...discuss with Chris on what can and cannot be done with this variable 

###Area measurements 
####Rank
```{r area}

# Define your response variables and corresponding predictor variable
area_response_vars <- c("TA", "MA", "CA")
GPR_predictor_var <- "GPRank"
MRC_predictor_var <- "MRC"

# Call the function
r_GPR_area_result_summaries <- area_mcmc_multiple(radius, area_response_vars, GPR_predictor_var)

r_GPR_area_result_summaries

# Call the function
r_MRC_area_result_summaries <- area_mcmc_multiple(radius, area_response_vars, MRC_predictor_var)

r_MRC_area_result_summaries
```

####Rain
```{r area}

# Define your response variables and corresponding predictor variable
area_response_vars <- c("TA", "MA", "CA")
GPDD_predictor_var <- "prop_droughtdays"
GR_predictor_var <- "gest_rain"

# Call the function
r_GPDD_area_result_summaries <- area_mcmc_multiple(radius, area_response_vars, GPDD_predictor_var)

# Call the function
r_GR_area_result_summaries <- area_mcmc_multiple(radius, area_response_vars, GR_predictor_var)

r_GR_area_result_summaries

```

###Moment of area measurements
####Rank
```{r I & J}

# Define your response variables and corresponding predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
GPR_predictor_var <- "GPRank"
MRC_predictor_var <- "MRC"

# Call the function
r_GPR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(radius, moment2nd_response_vars, GPR_predictor_var)

r_GPR_2ndmoment_result_summaries

# Call the function
r_MRC_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(radius, moment2nd_response_vars, MRC_predictor_var)

r_MRC_2ndmoment_result_summaries
```

####Rain
```{r I & J}

# Define your response variables and corresponding predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
GPDD_predictor_var <- "prop_droughtdays"
GR_predictor_var <- "gest_rain"

# Call the function
r_GPDD_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(radius, moment2nd_response_vars, GPDD_predictor_var)

r_GPDD_2ndmoment_result_summaries

# Call the function
r_GR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(radius, moment2nd_response_vars, GR_predictor_var)

r_GR_2ndmoment_result_summaries
```

###section moduli
####Rank
```{r Z}

# Define your response variables and corresponding predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
GPR_predictor_var <- "GPRank"
MRC_predictor_var <- "MRC"

# Call the function
r_GPR_moduli_result_summaries <- moduli_mcmc_multiple(radius, moduli_response_vars, GPR_predictor_var)

r_GPR_moduli_result_summaries

# Call the function
r_MRC_moduli_result_summaries <- moduli_mcmc_multiple(radius, moduli_response_vars, MRC_predictor_var)

r_MRC_moduli_result_summaries
```

####Rain
```{r Z}

# Define your response variables and corresponding predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
GPDD_predictor_var <- "prop_droughtdays"
GR_predictor_var <- "gest_rain"

# Call the function
r_GPDD_moduli_result_summaries <- moduli_mcmc_multiple(radius, moduli_response_vars, GPDD_predictor_var)

r_GPDD_moduli_result_summaries

# Call the function
r_GR_moduli_result_summaries <- moduli_mcmc_multiple(radius, moduli_response_vars, GR_predictor_var)

r_GR_moduli_result_summaries
```

##DIC Table radius
```{r DIC table rank & rain gestation}

dic_table_rank_r <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)



# Retrieve and store the DIC values for each model and bone
dic_table_rank_r$Model1 <- c(unlist(r_GPR_PCA$DIC),
                      unlist(r_GPR_area_result_summaries[[1]]$DIC),
                      unlist(r_GPR_area_result_summaries[[2]]$DIC),
                      unlist(r_GPR_area_result_summaries[[3]]$DIC),
                      unlist(r_GPR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(r_GPR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(r_GPR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(r_GPR_moduli_result_summaries[[1]]$DIC),
                      unlist(r_GPR_moduli_result_summaries[[2]]$DIC),
                      unlist(r_GPR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rank_r$Model2 <- c(unlist(h_MRC_PCA$DIC),
                      unlist(r_MRC_area_result_summaries[[1]]$DIC),
                      unlist(r_MRC_area_result_summaries[[2]]$DIC),
                      unlist(r_MRC_area_result_summaries[[3]]$DIC),
                      unlist(r_MRC_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(r_MRC_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(r_MRC_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(r_MRC_moduli_result_summaries[[1]]$DIC),
                      unlist(r_MRC_moduli_result_summaries[[2]]$DIC),
                      unlist(r_MRC_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rank_r) <- c("Geometric Properties", "Proportional Rank", "Ordinal Rank")


# Add a new column indicating which predictor variable is lower
dic_table_rank_r$Lower_Predictor <- ifelse(
  dic_table_rank_r$`Proportional Rank` < dic_table_rank_r$`Ordinal Rank`,
  "Proportion Rank", "Ordinal Rank"
)

print(dic_table_rank_r)


#write.csv(dic_table_rank_r, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rank_gest_r_CSG.csv", row.names=FALSE)

dic_table_rain_r <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)



# Retrieve and store the DIC values for each model and bone
dic_table_rain_r$Model1 <- c(unlist(r_GR_PCA$DIC),
                      unlist(r_GR_area_result_summaries[[1]]$DIC),
                      unlist(r_GR_area_result_summaries[[2]]$DIC),
                      unlist(r_GR_area_result_summaries[[3]]$DIC),
                      unlist(r_GR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(r_GR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(r_GR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(r_GR_moduli_result_summaries[[1]]$DIC),
                      unlist(r_GR_moduli_result_summaries[[2]]$DIC),
                      unlist(r_GR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rain_r$Model2 <- c(unlist(r_GPDD_PCA$DIC),
                      unlist(r_GPDD_area_result_summaries[[1]]$DIC),
                      unlist(r_GPDD_area_result_summaries[[2]]$DIC),
                      unlist(r_GPDD_area_result_summaries[[3]]$DIC),
                      unlist(r_GPDD_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(r_GPDD_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(r_GPDD_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(r_GPDD_moduli_result_summaries[[1]]$DIC),
                      unlist(r_GPDD_moduli_result_summaries[[2]]$DIC),
                      unlist(r_GPDD_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rain_r) <- c("Geometric Properties", "Cumulative Rainfall", "Proportion of Drought Days")

#write.csv(dic_table_rain_r, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rain_gest_r_CSG.csv", row.names=FALSE)

# Add a new column indicating which predictor variable is lower
dic_table_rain_r$Lower_Predictor <- ifelse(
  dic_table_rain_r$`Cumulative Rainfall` < dic_table_rain_r$`Proportion of Drought Days`,
  "Cumulative Rainfall", "Proportion of Drought Days"
)

print(dic_table_rain_r)
```


#Year 1

```{r year 1 subset}

radius_1 <- subset(radius, Age > .6)

```

#radius
##%CA
####Rank & Rainfall
```{r}
r_BPR_PCA <- PCA_mcmc(radius_1, "BPRank") 

r_BPR_PCA

r_MRB_PCA <- PCA_mcmc(radius_1, "MRB")

r_MRB_PCA

r_BPDD_PCA <- PCA_mcmc(radius_1, "prop_droughtdays_1year")

r_BPDD_PCA

r_BR_PCA <- PCA_mcmc(radius_1, "one_year_rain")

r_BR_PCA
```

Not good results for %CA...discuss with Chris on what can and cannot be done with this variable 

###Area measurements 
####Rank
```{r area}

# Define your response variables and correspondinB predictor variable
area_response_vars <- c("TA", "MA", "CA")
BPR_predictor_var <- "BPRank"
MRB_predictor_var <- "MRB"

# Call the function
r_BPR_area_result_summaries <- area_mcmc_multiple(radius_1, area_response_vars, BPR_predictor_var)

r_BPR_area_result_summaries

# Call the function
r_MRB_area_result_summaries <- area_mcmc_multiple(radius_1, area_response_vars, MRB_predictor_var)

r_MRB_area_result_summaries
```

####Rain
```{r area}

# Define your response variables and correspondinB predictor variable
area_response_vars <- c("TA", "MA", "CA")
BPDD_predictor_var <- "prop_droughtdays_1year"
BR_predictor_var <- "one_year_rain"

# Call the function
r_BPDD_area_result_summaries <- area_mcmc_multiple(radius_1, area_response_vars, BPDD_predictor_var)

# Call the function
r_BR_area_result_summaries <- area_mcmc_multiple(radius_1, area_response_vars, BR_predictor_var)

r_BR_area_result_summaries

```

##Moment of area measurements
####Rank
```{r I & J}

# Define your response variables and corresponding predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
BPR_predictor_var <- "BPRank"
MRB_predictor_var <- "MRB"

# Call the function
r_BPR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(radius_1, moment2nd_response_vars, BPR_predictor_var)

r_BPR_2ndmoment_result_summaries

# Call the function
r_MRB_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(radius_1, moment2nd_response_vars, MRB_predictor_var)

r_MRB_2ndmoment_result_summaries
```

####Rain
```{r I & J}

# Define your response variables and correspondinB predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
BPDD_predictor_var <- "prop_droughtdays_1year"
BR_predictor_var <- "one_year_rain"

# Call the function
r_BPDD_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(radius_1, moment2nd_response_vars, BPDD_predictor_var)

r_BPDD_2ndmoment_result_summaries

# Call the function
r_BR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(radius_1, moment2nd_response_vars, BR_predictor_var)

r_BR_2ndmoment_result_summaries
```

##section moduli
####Rank
```{r Z}

# Define your response variables and correspondinB predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
BPR_predictor_var <- "BPRank"
MRB_predictor_var <- "MRB"

# Call the function
r_BPR_moduli_result_summaries <- moduli_mcmc_multiple(radius_1, moduli_response_vars, BPR_predictor_var)

r_BPR_moduli_result_summaries

# Call the function
r_MRB_moduli_result_summaries <- moduli_mcmc_multiple(radius_1, moduli_response_vars, MRB_predictor_var)

r_MRB_moduli_result_summaries
```

####Rain
```{r Z}

# Define your response variables and correspondinB predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
BPDD_predictor_var <- "prop_droughtdays_1year"
BR_predictor_var <- "one_year_rain"

# Call the function
r_BPDD_moduli_result_summaries <- moduli_mcmc_multiple(radius_1, moduli_response_vars, BPDD_predictor_var)

r_BPDD_moduli_result_summaries

# Call the function
r_BR_moduli_result_summaries <- moduli_mcmc_multiple(radius_1, moduli_response_vars, BR_predictor_var)

r_BR_moduli_result_summaries
```

##DIC Table radius_1
```{r DIC table rank & rain Year 1}

dic_table_rank_1 <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)

# Retrieve and store the DIC values for each model and bone
dic_table_rank_1$Model1 <- c(unlist(r_BPR_PCA$DIC),
                      unlist(r_BPR_area_result_summaries[[1]]$DIC),
                      unlist(r_BPR_area_result_summaries[[2]]$DIC),
                      unlist(r_BPR_area_result_summaries[[3]]$DIC),
                      unlist(r_BPR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(r_BPR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(r_BPR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(r_BPR_moduli_result_summaries[[1]]$DIC),
                      unlist(r_BPR_moduli_result_summaries[[2]]$DIC),
                      unlist(r_BPR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rank_1$Model2 <- c(unlist(r_MRB_PCA$DIC),
                      unlist(r_MRB_area_result_summaries[[1]]$DIC),
                      unlist(r_MRB_area_result_summaries[[2]]$DIC),
                      unlist(r_MRB_area_result_summaries[[3]]$DIC),
                      unlist(r_MRB_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(r_MRB_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(r_MRB_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(r_MRB_moduli_result_summaries[[1]]$DIC),
                      unlist(r_MRB_moduli_result_summaries[[2]]$DIC),
                      unlist(r_MRB_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rank_1) <- c("Geometric Properties", "Proportional Rank", "Ordinal Rank")

# Add a new column indicatinB which predictor variable is lower
dic_table_rank_1$Lower_Predictor <- ifelse(
  dic_table_rank_1$`Proportional Rank` < dic_table_rank_1$`Ordinal Rank`,
  "Proportion Rank", "Ordinal Rank"
)

print(dic_table_rank_1)


write.csv(dic_table_rank_1, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rank_radius1_CSG.csv", row.names=FALSE)

dic_table_rain_1 <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)

# Retrieve and store the DIC values for each model and bone
dic_table_rain_1$Model1 <- c(unlist(r_BR_PCA$DIC),
                      unlist(r_BR_area_result_summaries[[1]]$DIC),
                      unlist(r_BR_area_result_summaries[[2]]$DIC),
                      unlist(r_BR_area_result_summaries[[3]]$DIC),
                      unlist(r_BR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(r_BR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(r_BR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(r_BR_moduli_result_summaries[[1]]$DIC),
                      unlist(r_BR_moduli_result_summaries[[2]]$DIC),
                      unlist(r_BR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rain_1$Model2 <- c(unlist(r_BPDD_PCA$DIC),
                      unlist(r_BPDD_area_result_summaries[[1]]$DIC),
                      unlist(r_BPDD_area_result_summaries[[2]]$DIC),
                      unlist(r_BPDD_area_result_summaries[[3]]$DIC),
                      unlist(r_BPDD_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(r_BPDD_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(r_BPDD_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(r_BPDD_moduli_result_summaries[[1]]$DIC),
                      unlist(r_BPDD_moduli_result_summaries[[2]]$DIC),
                      unlist(r_BPDD_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rain_1) <- c("Geometric Properties", "Cumulative Rainfall", "Proportion of Drought Days")

# Add a new column indicatinB which predictor variable is lower
dic_table_rain_1$Lower_Predictor <- ifelse(
  dic_table_rain_1$`Cumulative Rainfall` < dic_table_rain_1$`Proportion of Drought Days`,
  "Cumulative Rainfall", "Proportion of Drought Days"
)

print(dic_table_rain_1) 

write.csv(dic_table_rain_1, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rain_radius1_CSG.csv", row.names=FALSE)
```



#Femur

##Gestation
###%CA
####Rank & Rainfall
```{r}
f_GPR_PCA <- PCA_mcmc(femur, "GPRank")

f_GPR_PCA

f_MRC_PCA <- PCA_mcmc(femur, "MRC")

f_MRC_PCA

f_GPDD_PCA <- PCA_mcmc(femur, "prop_droughtdays")

f_GPDD_PCA

f_GR_PCA <- PCA_mcmc(femur, "gest_rain")

f_GR_PCA
```

Not good results for %CA...discuss with Chris on what can and cannot be done with this variable 

###Area measurements 
####Rank
```{r area}

# Define your response variables and corresponding predictor variable
area_response_vars <- c("TA", "MA", "CA")
GPR_predictor_var <- "GPRank"
MRC_predictor_var <- "MRC"

# Call the function
f_GPR_area_result_summaries <- area_mcmc_multiple(femur, area_response_vars, GPR_predictor_var)

f_GPR_area_result_summaries

# Call the function
f_MRC_area_result_summaries <- area_mcmc_multiple(femur, area_response_vars, MRC_predictor_var)

f_MRC_area_result_summaries
```

####Rain
```{r area}

# Define your response variables and corresponding predictor variable
area_response_vars <- c("TA", "MA", "CA")
GPDD_predictor_var <- "prop_droughtdays"
GR_predictor_var <- "gest_rain"

# Call the function
f_GPDD_area_result_summaries <- area_mcmc_multiple(femur, area_response_vars, GPDD_predictor_var)

# Call the function
f_GR_area_result_summaries <- area_mcmc_multiple(femur, area_response_vars, GR_predictor_var)

f_GR_area_result_summaries

```

###Moment of area measurements
####Rank
```{r I & J}

# Define your response variables and corresponding predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
GPR_predictor_var <- "GPRank"
MRC_predictor_var <- "MRC"

# Call the function
f_GPR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(femur, moment2nd_response_vars, GPR_predictor_var)

f_GPR_2ndmoment_result_summaries

# Call the function
f_MRC_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(femur, moment2nd_response_vars, MRC_predictor_var)

f_MRC_2ndmoment_result_summaries
```

####Rain
```{r I & J}

# Define your response variables and corresponding predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
GPDD_predictor_var <- "prop_droughtdays"
GR_predictor_var <- "gest_rain"

# Call the function
f_GPDD_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(femur, moment2nd_response_vars, GPDD_predictor_var)

f_GPDD_2ndmoment_result_summaries

# Call the function
f_GR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(femur, moment2nd_response_vars, GR_predictor_var)

f_GR_2ndmoment_result_summaries
```

###section moduli
####Rank
```{r Z}

# Define your response variables and corresponding predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
GPR_predictor_var <- "GPRank"
MRC_predictor_var <- "MRC"

# Call the function
f_GPR_moduli_result_summaries <- moduli_mcmc_multiple(femur, moduli_response_vars, GPR_predictor_var)

f_GPR_moduli_result_summaries

# Call the function
f_MRC_moduli_result_summaries <- moduli_mcmc_multiple(femur, moduli_response_vars, MRC_predictor_var)

f_MRC_moduli_result_summaries
```

####Rain
```{r Z}

# Define your response variables and corresponding predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
GPDD_predictor_var <- "prop_droughtdays"
GR_predictor_var <- "gest_rain"

# Call the function
f_GPDD_moduli_result_summaries <- moduli_mcmc_multiple(femur, moduli_response_vars, GPDD_predictor_var)

f_GPDD_moduli_result_summaries

# Call the function
f_GR_moduli_result_summaries <- moduli_mcmc_multiple(femur, moduli_response_vars, GR_predictor_var)

f_GR_moduli_result_summaries
```

##DIC Table Femur
```{r DIC table rank & rain gestation}

dic_table_rank_f <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)



# Retrieve and store the DIC values for each model and bone
dic_table_rank_f$Model1 <- c(unlist(f_GPR_PCA$DIC),
                      unlist(f_GPR_area_result_summaries[[1]]$DIC),
                      unlist(f_GPR_area_result_summaries[[2]]$DIC),
                      unlist(f_GPR_area_result_summaries[[3]]$DIC),
                      unlist(f_GPR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(f_GPR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(f_GPR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(f_GPR_moduli_result_summaries[[1]]$DIC),
                      unlist(f_GPR_moduli_result_summaries[[2]]$DIC),
                      unlist(f_GPR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rank_f$Model2 <- c(unlist(f_MRC_PCA$DIC),
                      unlist(f_MRC_area_result_summaries[[1]]$DIC),
                      unlist(f_MRC_area_result_summaries[[2]]$DIC),
                      unlist(f_MRC_area_result_summaries[[3]]$DIC),
                      unlist(f_MRC_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(f_MRC_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(f_MRC_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(f_MRC_moduli_result_summaries[[1]]$DIC),
                      unlist(f_MRC_moduli_result_summaries[[2]]$DIC),
                      unlist(f_MRC_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rank_f) <- c("Geometric Properties", "Proportional Rank", "Ordinal Rank")


# Add a new column indicating which predictor variable is lower
dic_table_rank_f$Lower_Predictor <- ifelse(
  dic_table_rank_f$`Proportional Rank` < dic_table_rank_f$`Ordinal Rank`,
  "Proportion Rank", "Ordinal Rank"
)

print(dic_table_rank_f)


#write.csv(dic_table_rank_f, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rank_gest_f_CSG.csv", row.names=FALSE)

dic_table_rain_f <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)



# Retrieve and store the DIC values for each model and bone
dic_table_rain_f$Model1 <- c(unlist(f_GR_PCA$DIC),
                      unlist(f_GR_area_result_summaries[[1]]$DIC),
                      unlist(f_GR_area_result_summaries[[2]]$DIC),
                      unlist(f_GR_area_result_summaries[[3]]$DIC),
                      unlist(f_GR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(f_GR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(f_GR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(f_GR_moduli_result_summaries[[1]]$DIC),
                      unlist(f_GR_moduli_result_summaries[[2]]$DIC),
                      unlist(f_GR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rain_f$Model2 <- c(unlist(f_GPDD_PCA$DIC),
                      unlist(f_GPDD_area_result_summaries[[1]]$DIC),
                      unlist(f_GPDD_area_result_summaries[[2]]$DIC),
                      unlist(f_GPDD_area_result_summaries[[3]]$DIC),
                      unlist(f_GPDD_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(f_GPDD_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(f_GPDD_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(f_GPDD_moduli_result_summaries[[1]]$DIC),
                      unlist(f_GPDD_moduli_result_summaries[[2]]$DIC),
                      unlist(f_GPDD_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rain_f) <- c("Geometric Properties", "Cumulative Rainfall", "Proportion of Drought Days")

# Add a new column indicating which predictor variable is lower
dic_table_rain_f$Lower_Predictor <- ifelse(
  dic_table_rain_f$`Cumulative Rainfall` < dic_table_rain_f$`Proportion of Drought Days`,
  "Cumulative Rainfall", "Proportion of Drought Days"
)

#write.csv(dic_table_rain_f, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rain_gest_f_CSG.csv", row.names=FALSE)

print(dic_table_rain_f)
```



#Year 1

```{r year 1 subset}

femur_1 <- subset(femur, Age > .6)

```

#Femur
##%CA
####Rank & Rainfall
```{r}
f_BPR_PCA <- PCA_mcmc(femur_1, "BPRank") 

f_BPR_PCA

f_MRB_PCA <- PCA_mcmc(femur_1, "MRB")

f_MRB_PCA

f_BPDD_PCA <- PCA_mcmc(femur_1, "prop_droughtdays_1year")

f_BPDD_PCA

f_BR_PCA <- PCA_mcmc(femur_1, "one_year_rain")

f_BR_PCA
```

Not good results for %CA...discuss with Chris on what can and cannot be done with this variable 

###Area measurements 
####Rank
```{r area}

# Define your response variables and correspondinB predictor variable
area_response_vars <- c("TA", "MA", "CA")
BPR_predictor_var <- "BPRank"
MRB_predictor_var <- "MRB"

# Call the function
f_BPR_area_result_summaries <- area_mcmc_multiple(femur_1, area_response_vars, BPR_predictor_var)

f_BPR_area_result_summaries

# Call the function
f_MRB_area_result_summaries <- area_mcmc_multiple(femur_1, area_response_vars, MRB_predictor_var)

f_MRB_area_result_summaries
```

####Rain
```{r area}

# Define your response variables and correspondinB predictor variable
area_response_vars <- c("TA", "MA", "CA")
BPDD_predictor_var <- "prop_droughtdays_1year"
BR_predictor_var <- "one_year_rain"

# Call the function
f_BPDD_area_result_summaries <- area_mcmc_multiple(femur_1, area_response_vars, BPDD_predictor_var)

# Call the function
f_BR_area_result_summaries <- area_mcmc_multiple(femur_1, area_response_vars, BR_predictor_var)

f_BR_area_result_summaries

```

##Moment of area measurements
####Rank
```{r I & J}

# Define your response variables and corresponding predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
BPR_predictor_var <- "BPRank"
MRB_predictor_var <- "MRB"

# Call the function
f_BPR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(femur_1, moment2nd_response_vars, BPR_predictor_var)

f_BPR_2ndmoment_result_summaries

# Call the function
f_MRB_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(femur_1, moment2nd_response_vars, MRB_predictor_var)

f_MRB_2ndmoment_result_summaries
```

####Rain
```{r I & J}

# Define your response variables and correspondinB predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
BPDD_predictor_var <- "prop_droughtdays_1year"
BR_predictor_var <- "one_year_rain"

# Call the function
f_BPDD_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(femur_1, moment2nd_response_vars, BPDD_predictor_var)

f_BPDD_2ndmoment_result_summaries

# Call the function
f_BR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(femur_1, moment2nd_response_vars, BR_predictor_var)

f_BR_2ndmoment_result_summaries
```

##section moduli
####Rank
```{r Z}

# Define your response variables and correspondinB predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
BPR_predictor_var <- "BPRank"
MRB_predictor_var <- "MRB"

# Call the function
f_BPR_moduli_result_summaries <- moduli_mcmc_multiple(femur_1, moduli_response_vars, BPR_predictor_var)

f_BPR_moduli_result_summaries

# Call the function
f_MRB_moduli_result_summaries <- moduli_mcmc_multiple(femur_1, moduli_response_vars, MRB_predictor_var)

f_MRB_moduli_result_summaries
```

####Rain
```{r Z}

# Define your response variables and correspondinB predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
BPDD_predictor_var <- "prop_droughtdays_1year"
BR_predictor_var <- "one_year_rain"

# Call the function
f_BPDD_moduli_result_summaries <- moduli_mcmc_multiple(femur_1, moduli_response_vars, BPDD_predictor_var)

f_BPDD_moduli_result_summaries

# Call the function
f_BR_moduli_result_summaries <- moduli_mcmc_multiple(femur_1, moduli_response_vars, BR_predictor_var)

f_BR_moduli_result_summaries
```

##DIC Table femur_1
```{r DIC table rank & rain Year 1}

dic_table_rank_1 <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)

# Retrieve and store the DIC values for each model and bone
dic_table_rank_1$Model1 <- c(unlist(f_BPR_PCA$DIC),
                      unlist(f_BPR_area_result_summaries[[1]]$DIC),
                      unlist(f_BPR_area_result_summaries[[2]]$DIC),
                      unlist(f_BPR_area_result_summaries[[3]]$DIC),
                      unlist(f_BPR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(f_BPR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(f_BPR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(f_BPR_moduli_result_summaries[[1]]$DIC),
                      unlist(f_BPR_moduli_result_summaries[[2]]$DIC),
                      unlist(f_BPR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rank_1$Model2 <- c(unlist(f_MRB_PCA$DIC),
                      unlist(f_MRB_area_result_summaries[[1]]$DIC),
                      unlist(f_MRB_area_result_summaries[[2]]$DIC),
                      unlist(f_MRB_area_result_summaries[[3]]$DIC),
                      unlist(f_MRB_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(f_MRB_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(f_MRB_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(f_MRB_moduli_result_summaries[[1]]$DIC),
                      unlist(f_MRB_moduli_result_summaries[[2]]$DIC),
                      unlist(f_MRB_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rank_1) <- c("Geometric Properties", "Proportional Rank", "Ordinal Rank")

# Add a new column indicatinB which predictor variable is lower
dic_table_rank_1$Lower_Predictor <- ifelse(
  dic_table_rank_1$`Proportional Rank` < dic_table_rank_1$`Ordinal Rank`,
  "Proportion Rank", "Ordinal Rank"
)

print(dic_table_rank_1)


#write.csv(dic_table_rank_1, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rank_femur1_CSG.csv", row.names=FALSE)

dic_table_rain_1 <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)

# Retrieve and store the DIC values for each model and bone
dic_table_rain_1$Model1 <- c(unlist(f_BR_PCA$DIC),
                      unlist(f_BR_area_result_summaries[[1]]$DIC),
                      unlist(f_BR_area_result_summaries[[2]]$DIC),
                      unlist(f_BR_area_result_summaries[[3]]$DIC),
                      unlist(f_BR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(f_BR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(f_BR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(f_BR_moduli_result_summaries[[1]]$DIC),
                      unlist(f_BR_moduli_result_summaries[[2]]$DIC),
                      unlist(f_BR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rain_1$Model2 <- c(unlist(f_BPDD_PCA$DIC),
                      unlist(f_BPDD_area_result_summaries[[1]]$DIC),
                      unlist(f_BPDD_area_result_summaries[[2]]$DIC),
                      unlist(f_BPDD_area_result_summaries[[3]]$DIC),
                      unlist(f_BPDD_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(f_BPDD_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(f_BPDD_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(f_BPDD_moduli_result_summaries[[1]]$DIC),
                      unlist(f_BPDD_moduli_result_summaries[[2]]$DIC),
                      unlist(f_BPDD_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rain_1) <- c("Geometric Properties", "Cumulative Rainfall", "Proportion of Drought Days")

# Add a new column indicatinB which predictor variable is lower
dic_table_rain_1$Lower_Predictor <- ifelse(
  dic_table_rain_1$`Cumulative Rainfall` < dic_table_rain_1$`Proportion of Drought Days`,
  "Cumulative Rainfall", "Proportion of Drought Days"
)

print(dic_table_rain_1) 

#write.csv(dic_table_rain_1, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rain_femur1_CSG.csv", row.names=FALSE)
```


#Tibia
##Gestation
####%CA
#####Rank & Rainfall
```{r}
t_GPR_PCA <- PCA_mcmc(tibia, "GPRank")

t_GPR_PCA

t_MRC_PCA <- PCA_mcmc(tibia, "MRC")

t_MRC_PCA

t_GPDD_PCA <- PCA_mcmc(tibia, "prop_droughtdays")

t_GPDD_PCA

t_GR_PCA <- PCA_mcmc(tibia, "gest_rain")

t_GR_PCA
```

Not good results for %CA...discuss with Chris on what can and cannot be done with this variable 

####Area measurements 
#####Rank
```{r area}

# Define your response variables and corresponding predictor variable
area_response_vars <- c("TA", "MA", "CA")
GPR_predictor_var <- "GPRank"
MRC_predictor_var <- "MRC"

# Call the function
t_GPR_area_result_summaries <- area_mcmc_multiple(tibia, area_response_vars, GPR_predictor_var)

t_GPR_area_result_summaries

# Call the function
t_MRC_area_result_summaries <- area_mcmc_multiple(tibia, area_response_vars, MRC_predictor_var)

t_MRC_area_result_summaries
```

#####Rain
```{r area}

# Define your response variables and corresponding predictor variable
area_response_vars <- c("TA", "MA", "CA")
GPDD_predictor_var <- "prop_droughtdays"
GR_predictor_var <- "gest_rain"

# Call the function
t_GPDD_area_result_summaries <- area_mcmc_multiple(tibia, area_response_vars, GPDD_predictor_var)

# Call the function
t_GR_area_result_summaries <- area_mcmc_multiple(tibia, area_response_vars, GR_predictor_var)

t_GR_area_result_summaries

```

####Moment of area measurements
#####Rank
```{r I & J}

# Define your response variables and corresponding predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
GPR_predictor_var <- "GPRank"
MRC_predictor_var <- "MRC"

# Call the function
t_GPR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(tibia, moment2nd_response_vars, GPR_predictor_var)

t_GPR_2ndmoment_result_summaries

# Call the function
t_MRC_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(tibia, moment2nd_response_vars, MRC_predictor_var)

t_MRC_2ndmoment_result_summaries
```

#####Rain
```{r I & J}

# Define your response variables and corresponding predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
GPDD_predictor_var <- "prop_droughtdays"
GR_predictor_var <- "gest_rain"

# Call the function
t_GPDD_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(tibia, moment2nd_response_vars, GPDD_predictor_var)

t_GPDD_2ndmoment_result_summaries

# Call the function
t_GR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(tibia, moment2nd_response_vars, GR_predictor_var)

t_GR_2ndmoment_result_summaries
```

####section moduli
#####Rank
```{r Z}

# Define your response variables and corresponding predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
GPR_predictor_var <- "GPRank"
MRC_predictor_var <- "MRC"

# Call the function
t_GPR_moduli_result_summaries <- moduli_mcmc_multiple(tibia, moduli_response_vars, GPR_predictor_var)

t_GPR_moduli_result_summaries

# Call the function
t_MRC_moduli_result_summaries <- moduli_mcmc_multiple(tibia, moduli_response_vars, MRC_predictor_var)

t_MRC_moduli_result_summaries
```

#####Rain
```{r Z}

# Define your response variables and corresponding predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
GPDD_predictor_var <- "prop_droughtdays"
GR_predictor_var <- "gest_rain"

# Call the function
t_GPDD_moduli_result_summaries <- moduli_mcmc_multiple(tibia, moduli_response_vars, GPDD_predictor_var)

t_GPDD_moduli_result_summaries

# Call the function
t_GR_moduli_result_summaries <- moduli_mcmc_multiple(tibia, moduli_response_vars, GR_predictor_var)

t_GR_moduli_result_summaries
```

##DIC Table Tibia
```{r DIC table rank & rain gestation}

dic_table_rank_t <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)



# Retrieve and store the DIC values for each model and bone
dic_table_rank_t$Model1 <- c(unlist(t_GPR_PCA$DIC),
                      unlist(t_GPR_area_result_summaries[[1]]$DIC),
                      unlist(t_GPR_area_result_summaries[[2]]$DIC),
                      unlist(t_GPR_area_result_summaries[[3]]$DIC),
                      unlist(t_GPR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(t_GPR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(t_GPR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(t_GPR_moduli_result_summaries[[1]]$DIC),
                      unlist(t_GPR_moduli_result_summaries[[2]]$DIC),
                      unlist(t_GPR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rank_t$Model2 <- c(unlist(t_MRC_PCA$DIC),
                      unlist(t_MRC_area_result_summaries[[1]]$DIC),
                      unlist(t_MRC_area_result_summaries[[2]]$DIC),
                      unlist(t_MRC_area_result_summaries[[3]]$DIC),
                      unlist(t_MRC_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(t_MRC_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(t_MRC_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(t_MRC_moduli_result_summaries[[1]]$DIC),
                      unlist(t_MRC_moduli_result_summaries[[2]]$DIC),
                      unlist(t_MRC_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rank_t) <- c("Geometric Properties", "Proportional Rank", "Ordinal Rank")


# Add a new column indicating which predictor variable is lower
dic_table_rank_t$Lower_Predictor <- ifelse(
  dic_table_rank_t$`Proportional Rank` < dic_table_rank_t$`Ordinal Rank`,
  "Proportion Rank", "Ordinal Rank"
)

print(dic_table_rank_t)


#write.csv(dic_table_rank_t, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rank_gest_t_CSG.csv", row.names=FALSE)

dic_table_rain_t <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)



# Retrieve and store the DIC values for each model and bone
dic_table_rain_t$Model1 <- c(unlist(t_GR_PCA$DIC),
                      unlist(t_GR_area_result_summaries[[1]]$DIC),
                      unlist(t_GR_area_result_summaries[[2]]$DIC),
                      unlist(t_GR_area_result_summaries[[3]]$DIC),
                      unlist(t_GR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(t_GR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(t_GR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(t_GR_moduli_result_summaries[[1]]$DIC),
                      unlist(t_GR_moduli_result_summaries[[2]]$DIC),
                      unlist(t_GR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rain_t$Model2 <- c(unlist(t_GPDD_PCA$DIC),
                      unlist(t_GPDD_area_result_summaries[[1]]$DIC),
                      unlist(t_GPDD_area_result_summaries[[2]]$DIC),
                      unlist(t_GPDD_area_result_summaries[[3]]$DIC),
                      unlist(t_GPDD_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(t_GPDD_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(t_GPDD_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(t_GPDD_moduli_result_summaries[[1]]$DIC),
                      unlist(t_GPDD_moduli_result_summaries[[2]]$DIC),
                      unlist(t_GPDD_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rain_t) <- c("Geometric Properties", "Cumulative Rainfall", "Proportion of Drought Days")

# Add a new column indicating which predictor variable is lower
dic_table_rain_t$Lower_Predictor <- ifelse(
  dic_table_rain_t$`Cumulative Rainfall` < dic_table_rain_t$`Proportion of Drought Days`,
  "Cumulative Rainfall", "Proportion of Drought Days"
)

#write.csv(dic_table_rain_t, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rain_gest_t_CSG.csv", row.names=FALSE)

print(dic_table_rain_t)
```

#Year 1

```{r year 1 subset}

tibia_1 <- subset(tibia, Age > .6)

```

#Tibia
##%CA
####Rank & Rainfall
```{r}
t_BPR_PCA <- PCA_mcmc(tibia_1, "BPRank") 

t_BPR_PCA

t_MRB_PCA <- PCA_mcmc(tibia_1, "MRB")

t_MRB_PCA

t_BPDD_PCA <- PCA_mcmc(tibia_1, "prop_droughtdays_1year")

t_BPDD_PCA

t_BR_PCA <- PCA_mcmc(tibia_1, "one_year_rain")

t_BR_PCA
```

Not good results for %CA...discuss with Chris on what can and cannot be done with this variable 

###Area measurements 
####Rank
```{r area}

# Define your response variables and correspondinB predictor variable
area_response_vars <- c("TA", "MA", "CA")
BPR_predictor_var <- "BPRank"
MRB_predictor_var <- "MRB"

# Call the function
t_BPR_area_result_summaries <- area_mcmc_multiple(tibia_1, area_response_vars, BPR_predictor_var)

t_BPR_area_result_summaries

# Call the function
t_MRB_area_result_summaries <- area_mcmc_multiple(tibia_1, area_response_vars, MRB_predictor_var)

t_MRB_area_result_summaries
```

####Rain
```{r area}

# Define your response variables and correspondinB predictor variable
area_response_vars <- c("TA", "MA", "CA")
BPDD_predictor_var <- "prop_droughtdays_1year"
BR_predictor_var <- "one_year_rain"

# Call the function
t_BPDD_area_result_summaries <- area_mcmc_multiple(tibia_1, area_response_vars, BPDD_predictor_var)

# Call the function
t_BR_area_result_summaries <- area_mcmc_multiple(tibia_1, area_response_vars, BR_predictor_var)

t_BR_area_result_summaries

```

##Moment of area measurements
####Rank
```{r I & J}

# Define your response variables and corresponding predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
BPR_predictor_var <- "BPRank"
MRB_predictor_var <- "MRB"

# Call the function
t_BPR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(tibia_1, moment2nd_response_vars, BPR_predictor_var)

t_BPR_2ndmoment_result_summaries

# Call the function
t_MRB_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(tibia_1, moment2nd_response_vars, MRB_predictor_var)

t_MRB_2ndmoment_result_summaries
```

####Rain
```{r I & J}

# Define your response variables and correspondinB predictor variable
moment2nd_response_vars <- c("Ix", "Iy", "J")
BPDD_predictor_var <- "prop_droughtdays_1year"
BR_predictor_var <- "one_year_rain"

# Call the function
t_BPDD_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(tibia_1, moment2nd_response_vars, BPDD_predictor_var)

t_BPDD_2ndmoment_result_summaries

# Call the function
t_BR_2ndmoment_result_summaries <- moment2nd_mcmc_multiple(tibia_1, moment2nd_response_vars, BR_predictor_var)

t_BR_2ndmoment_result_summaries
```

##section moduli
####Rank
```{r Z}

# Define your response variables and correspondinB predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
BPR_predictor_var <- "BPRank"
MRB_predictor_var <- "MRB"

# Call the function
t_BPR_moduli_result_summaries <- moduli_mcmc_multiple(tibia_1, moduli_response_vars, BPR_predictor_var)

t_BPR_moduli_result_summaries

# Call the function
t_MRB_moduli_result_summaries <- moduli_mcmc_multiple(tibia_1, moduli_response_vars, MRB_predictor_var)

t_MRB_moduli_result_summaries
```

####Rain
```{r Z}

# Define your response variables and correspondinB predictor variable
moduli_response_vars <- c("Zx", "Zy", "Zp")
BPDD_predictor_var <- "prop_droughtdays_1year"
BR_predictor_var <- "one_year_rain"

# Call the function
t_BPDD_moduli_result_summaries <- moduli_mcmc_multiple(tibia_1, moduli_response_vars, BPDD_predictor_var)

t_BPDD_moduli_result_summaries

# Call the function
t_BR_moduli_result_summaries <- moduli_mcmc_multiple(tibia_1, moduli_response_vars, BR_predictor_var)

t_BR_moduli_result_summaries
```

##DIC Table tibia_1
```{r DIC table rank & rain Year 1}

dic_table_rank_1 <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)

# Retrieve and store the DIC values for each model and bone
dic_table_rank_1$Model1 <- c(unlist(t_BPR_PCA$DIC),
                      unlist(t_BPR_area_result_summaries[[1]]$DIC),
                      unlist(t_BPR_area_result_summaries[[2]]$DIC),
                      unlist(t_BPR_area_result_summaries[[3]]$DIC),
                      unlist(t_BPR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(t_BPR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(t_BPR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(t_BPR_moduli_result_summaries[[1]]$DIC),
                      unlist(t_BPR_moduli_result_summaries[[2]]$DIC),
                      unlist(t_BPR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rank_1$Model2 <- c(unlist(t_MRB_PCA$DIC),
                      unlist(t_MRB_area_result_summaries[[1]]$DIC),
                      unlist(t_MRB_area_result_summaries[[2]]$DIC),
                      unlist(t_MRB_area_result_summaries[[3]]$DIC),
                      unlist(t_MRB_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(t_MRB_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(t_MRB_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(t_MRB_moduli_result_summaries[[1]]$DIC),
                      unlist(t_MRB_moduli_result_summaries[[2]]$DIC),
                      unlist(t_MRB_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rank_1) <- c("Geometric Properties", "Proportional Rank", "Ordinal Rank")

# Add a new column indicating which predictor variable is lower
dic_table_rank_1$Lower_Predictor <- ifelse(
  dic_table_rank_1$`Proportional Rank` < dic_table_rank_1$`Ordinal Rank`,
  "Proportion Rank", "Ordinal Rank"
)

print(dic_table_rank_1)


#write.csv(dic_table_rank_1, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rank_tibia1_CSG.csv", row.names=FALSE)

dic_table_rain_1 <- data.frame(
  Bone = c("%CA", "TA", "MA", "CA", "Ix", "Iy", "J", "Zx", "Zy", "Zp"),
  Model1 = NA,
  Model2 = NA
)

# Retrieve and store the DIC values for each model and bone
dic_table_rain_1$Model1 <- c(unlist(t_BR_PCA$DIC),
                      unlist(t_BR_area_result_summaries[[1]]$DIC),
                      unlist(t_BR_area_result_summaries[[2]]$DIC),
                      unlist(t_BR_area_result_summaries[[3]]$DIC),
                      unlist(t_BR_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(t_BR_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(t_BR_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(t_BR_moduli_result_summaries[[1]]$DIC),
                      unlist(t_BR_moduli_result_summaries[[2]]$DIC),
                      unlist(t_BR_moduli_result_summaries[[3]]$DIC)
                      )

dic_table_rain_1$Model2 <- c(unlist(t_BPDD_PCA$DIC),
                      unlist(t_BPDD_area_result_summaries[[1]]$DIC),
                      unlist(t_BPDD_area_result_summaries[[2]]$DIC),
                      unlist(t_BPDD_area_result_summaries[[3]]$DIC),
                      unlist(t_BPDD_2ndmoment_result_summaries[[1]]$DIC),
                      unlist(t_BPDD_2ndmoment_result_summaries[[2]]$DIC),
                      unlist(t_BPDD_2ndmoment_result_summaries[[3]]$DIC),
                      unlist(t_BPDD_moduli_result_summaries[[1]]$DIC),
                      unlist(t_BPDD_moduli_result_summaries[[2]]$DIC),
                      unlist(t_BPDD_moduli_result_summaries[[3]]$DIC)
                      )

colnames(dic_table_rain_1) <- c("Geometric Properties", "Cumulative Rainfall", "Proportion of Drought Days")

# Add a new column indicating which predictor variable is lower
dic_table_rain_1$Lower_Predictor <- ifelse(
  dic_table_rain_1$`Cumulative Rainfall` < dic_table_rain_1$`Proportion of Drought Days`,
  "Cumulative Rainfall", "Proportion of Drought Days"
)

print(dic_table_rain_1) 

#write.csv(dic_table_rain_1, "C:/Users/ktuos/Desktop/ABRP Excel Files/dic_table_rain_tibia1_CSG.csv", row.names=FALSE)
```


