---
title: "ABRP CSG SMA"
author: "Kristen Tuosto"
date: "2023-03-22"
output: html_document
---

```{r reading in packages and df}  
library(ggplot2)
library(dplyr)
library(tidyverse)

Longbones <- read.csv("C:/Users/ktuos/Desktop/ABRP Excel Files/ABRP_Master_List_3_24_2023.csv")

```

```{r filter function codes}

#Filter function without consideration for rainfall or rank variables 

filter_sample <- function(df, x) {
 x <- filter(df, Bone.Code == x)
 x[x==""] <- NA
# x[x=="U"] <- NA
 x <- x %>% drop_na(MA, Age, Sex, FDML.BM.kg)
 x$Sex <- as.factor(x$Sex)
 x$Age <- as.numeric(x$Age)
  x <- data.frame(x$ABRP_ID, x$Sex, x$Age, x$Age_Class, x$MXL, x$FDML.BM.kg, x$TA, x$MA, x$CA, x$Ix, x$Iy, x$J, x$P.CA, x$Zx, x$Zy, x$Zp, x$xr_mCT)
 x <- x %>% rename("ABRP_ID" = "x.ABRP_ID",
                   "Sex" = "x.Sex",
                   "Age" = "x.Age",
                   "Age_Class" = "x.Age_Class",
                   "MXL" = "x.MXL",
                   "BM" = "x.FDML.BM.kg",
                   "TA" = "x.TA",
                   "MA" = "x.MA",
                   "CA" = "x.CA",
                   "P.CA" = "x.P.CA",
                   "Ix" = "x.Ix",
                   "Iy" = "x.Iy",
                   "J" = "x.J",
                   "Zx" = "x.Zx",
                   "Zy" = "x.Zy",
                   "Zp" = "x.Zp",
                   "xr_mCT" = "x.xr_mCT")
 return(data.frame(x))
}

#Filter function with consideration for rainfall and rank variables for gestation (code will be used for prediction testing)

filter_sample_g <- function(df, x) {
 x <- filter(df, Bone.Code == x)
 x[x==""] <- NA
 x[x=="U"] <- NA
 x <- x %>% drop_na(MA, MRC, Age, gest_rain, Sex, FDML.BM.kg)
 x$Sex <- as.factor(x$Sex)
 x$Age <- as.numeric(x$Age)
 x$gest_rain <- as.numeric(x$gest_rain)
 x$MRC <- as.numeric(x$MRC)
 x$n_drought_months_g <- as.numeric(x$n_drought_months_g)
 x$GPRank <- as.numeric(x$GPRank)
  x <- data.frame(x$ABRP_ID, x$Sex, x$Age, x$Age_Class, x$DIL, x$MRC, x$GPRank, x$gest_rain, x$n_drought_months_g, x$prop_droughtdays, x$MXL, x$FDML.BM.kg, x$TA, x$MA, x$CA, x$Ix, x$Iy, x$J, x$P.CA, x$Zx, x$Zy, x$Zp, x$xr_mCT)
 x <- x %>% rename("ABRP_ID" = "x.ABRP_ID",
                   "Sex" = "x.Sex",
                   "Age" = "x.Age",
                   "Age_Class" = "x.Age_Class",
                   "MRC" = "x.MRC",
                   "GPRank" = "x.GPRank",
                   "gest_rain" = "x.gest_rain",
                   "n_drought_months_g" = "x.n_drought_months_g",
                   "prop_droughtdays" = "x.prop_droughtdays",
                   "MXL" = "x.MXL",
                   "BM" = "x.FDML.BM.kg",
                   "TA" = "x.TA",
                   "MA" = "x.MA",
                   "CA" = "x.CA",
                   "P.CA" = "x.P.CA",
                   "Ix" = "x.Ix",
                   "Iy" = "x.Iy",
                   "J" = "x.J",
                   "Zx" = "x.Zx",
                   "Zy" = "x.Zy",
                   "Zp" = "x.Zp",
                   "xr_mCT" = "x.xr_mCT")
 return(data.frame(x))
}

#Filter function with consideration for rainfall and rank variables for 1st year (code will be used for prediction testing)

filter_sample_y1 <- function(df, x) {
 x <- filter(df, Bone.Code == x)
 x[x==""] <- NA
 x <- x %>% drop_na(MA, MRB, Age, one_year_rain, FDML.BM.kg)
 x <- subset(x, Age > .6)
 #x <- subset(x, one_year_rain < 450)
 x$Sex <- as.factor(x$Sex)
 x$Age <- as.numeric(x$Age)
 x$one_year_rain <- as.numeric(x$one_year_rain)
  x <- data.frame(x$ABRP_ID, x$Sex, x$Age, x$MRB, x$BPRank, x$one_year_rain, x$n_drought_months_year1, x$prop_droughtdays_1year, x$MXL, x$FDML.BM.kg, x$TA, x$MA, x$CA, x$Ix, x$Iy, x$J, x$P.CA, x$Zx, x$Zy, x$Zp, x$xr_mCT)
 x <- x %>% rename("ABRP_ID" = "x.ABRP_ID",
                   "Sex" = "x.Sex",
                   "Age" = "x.Age",
                   "MRB" = "x.MRB",
                   "BPRank" = "x.BPRank",
                   "one_year_rain" = "x.one_year_rain",
                   "n_drought_months_year1" = "x.n_drought_months_year1",
                   "prop_droughtdays_1year" = "x.prop_droughtdays_1year",
                   "MXL" = "x.MXL",
                   "BM" = "x.FDML.BM.kg",
                   "TA" = "x.TA",
                   "MA" = "x.MA",
                   "CA" = "x.CA",
                   "P.CA" = "x.P.CA",
                   "Ix" = "x.Ix",
                   "Iy" = "x.Iy",
                   "J" = "x.J",
                   "Zx" = "x.Zx",
                   "Zy" = "x.Zy",
                   "Zp" = "x.Zp",
                   "xr_mCT" = "x.xr_mCT")
 return(data.frame(x))
}

```



```{r filter sample - full}

humerus <- filter_sample(Longbones, 'Humerus')

radius <- filter_sample(Longbones, 'Radius')

femur <- filter_sample(Longbones, 'Femur')

tibia <- filter_sample(Longbones, 'Tibia')

```

#SMA function code
```{r SMA functions by area, moment of area, modulus, %CA}
library(lmodel2)
library(plotly)

#Area
SMA_fun <- function(df, x) { #areas
  p <- lmodel2(log(x)~log(BM), data=df, "interval", "interval", 99) #y ~ x 
  print(p)
  return(p)
}

#Moment of area
SMA_fun1 <- function(df, x) { #section moduli
  p <- lmodel2(log(x)~log(BM*MXL), data=df, "interval", "interval", 99) #y ~ x 
  print(p)
  return(p)
}

#Modulus 
SMA_fun2 <- function(df, x) { #second moments of area
  p <- lmodel2(log(x)~log(BM*MXL^2), data=df, "interval", "interval", 99) #y ~ x 
  print(p)
  return(p)
}

#%CA
P.CA_SMA <-  function(df) {
  p <- lmodel2(P.CA ~ Age, data=df, "interval", "interval", 99) #y ~ x 
  print(p)
  return(p)
}

```

```{r}
qplot(x=Age, y=log(BM), color = Sex, data = femur) + geom_smooth() + geom_point() + theme_classic() + labs(x="Age (years)", y="log(Body Mass)") + scale_colour_discrete(labels = c("Female", "Male", "Unknown")) + labs(color = "Sex") 

```


#SMA plotting function code
```{r SMA plot functions}

SMA_plots <- function(df, y, a, b) {
  Log_plot <- ggplot(aes(y=log(y), x=log(BM)), data=df) + geom_point(aes(color = Sex), size =3) + theme_classic()
  plot <- Log_plot + geom_abline(aes(intercept = a, slope = b), size=1.2, show.legend = TRUE) 
  return(plot)
}

SMA_plots1 <- function(df, y, a, b) {
  Log_plot <- ggplot(aes(y=log(y), x=log(BM*MXL)), data=df) + geom_point(aes(color = Sex), size =3)
  plot <- Log_plot + geom_abline(aes(intercept = a, slope = b, color="SMA"), size=1.2, show.legend = TRUE) 
  return(plot)
}

SMA_plots2 <- function(df, y, a, b) {
  Log_plot <- ggplot(aes(y=log(y), x=log(BM*MXL^2)), data=df) + geom_point(aes(color = Sex), size =3)
  plot <- Log_plot + geom_abline(aes(intercept = a, slope = b, color="SMA"), size=1.2, show.legend = TRUE) 
  return(plot)
}


P.CA_plot <- function(df, a, b) {
  plot1 <- ggplot(aes(y=P.CA, x=Age), data=df) + geom_point(aes(color = Sex), size =3) 
  plot <- plot1 + geom_abline(aes(intercept = a, slope = b, color="SMA"), size=1.2, show.legend = TRUE) 
  return(plot)
}

```

#Humerus 
```{r}
TA_humerus <- SMA_fun(humerus, humerus$TA)

plot(TA_humerus, method = "SMA") # SMA plot

humerus_TA <- SMA_plots(humerus, humerus$TA, 2.892465,	0.7348611) #Code for an interactive plot/regular plot

humerus_TA + labs(y="log(Humerus TA)")

ggplotly(humerus_TA) # Interactive plot 

```

```{r}
MA_humerus <- SMA_fun(humerus, humerus$MA)

plot(MA_humerus, method = "SMA") # SMA plot

humerus_MA<- SMA_plots(humerus, humerus$MA, 1.708874,	0.8319917) #Code for an interactive plot

humerus_MA + labs(y="log(Humerus MA)")

ggplotly(humerus_MA) # Interactive plot 

```

```{r}
CA_humerus <- SMA_fun(humerus, humerus$CA)

plot(CA_humerus, method = "SMA") # SMA plot

humerus_CA <- SMA_plots(humerus, humerus$CA, 2.451837,	0.7106097) #Code for an interactive plot 

humerus_CA + labs(y="log(Humerus CA)")

ggplotly(humerus_CA) # Interactive plot 

```


```{r}

Ix_humerus <- SMA_fun2(humerus, humerus$Ix)

plot(Ix_humerus, method = "SMA") # SMA plot

humerus_Ix <- SMA_plots2(humerus, humerus$Ix, -4.006560,	0.8182380	) #Code for an interactive plot

ggplotly(humerus_Ix) # Interactive plot 

```


```{r}
Iy_humerus <- SMA_fun2(humerus, humerus$Iy)

plot(Iy_humerus, method = "SMA") # SMA plot

humerus_Iy <- SMA_plots2(humerus, humerus$Iy, -3.557639,	0.8059244	) #Code for an interactive plot 

ggplotly(humerus_Iy) # Interactive plot 

```

```{r}
J_humerus <- SMA_fun2(humerus, humerus$J)

plot(J_humerus, method = "SMA") # SMA plot

humerus_J <- SMA_plots2(humerus, humerus$J, -3.058409,	0.8109203) #Code for an interactive plot

ggplotly(humerus_J) # Interactive plot 

```

```{r}
Zx_humerus <- SMA_fun1(humerus, humerus$Zx)

plot(Zx_humerus, method = "SMA") # SMA plot

humerus_Zx <- SMA_plots1(humerus, humerus$Zx, -1.180539,	0.7812360) #Code for an interactive plot

ggplotly(humerus_Zx) # Interactive plot 
```

```{r}
Zy_humerus <- SMA_fun1(humerus, humerus$Zy)

plot(Zy_humerus, method = "SMA") # SMA plot

humerus_Zy <- SMA_plots1(humerus, humerus$Zy, -0.9520352,	0.7718883	) #Code for an interactive plot

ggplotly(humerus_Zy) # Interactive plot 
```

```{r}
Zp_humerus <- SMA_fun1(humerus, humerus$Zp)

plot(Zp_humerus, method = "SMA") # SMA plot

humerus_Zp <- SMA_plots1(humerus, humerus$Zp, -0.3278513,	0.7654265) #Code for an interactive plot

ggplotly(humerus_Zp) # Interactive plot 
```


```{r}
P.CA_humerus <- P.CA_SMA(humerus) 

plot(P.CA_humerus, method = "SMA") # SMA plot

humerus_P.CA <- P.CA_plot(humerus, 71.03178,	-0.9842820) #Code for an interactive plot

ggplotly(humerus_P.CA) # Interactive plot 

```


#General notes for the humerus: 


#femur 
```{r}
TA_femur <- SMA_fun(femur, femur$TA)

plot(TA_femur, method = "SMA") # SMA plot

femur_TA <- SMA_plots(femur, femur$TA, 2.953807,	0.7715318) #Code for an interactive plot 

ggplotly(femur_TA) # Interactive plot 

```

```{r}
MA_femur <- SMA_fun(femur, femur$MA)

plot(MA_femur, method = "SMA") # SMA plot

femur_MA <- SMA_plots(femur, femur$MA, 1.744768,	0.8542631) #Code for an interactive plot

ggplotly(femur_MA) # Interactive plot 

```

```{r}
CA_femur <- SMA_fun(femur, femur$CA)

plot(CA_femur, method = "SMA") # SMA plot

femur_CA <- SMA_plots(femur, femur$CA, 2.505304,	0.7658813	) #Code for an interactive plot 

ggplotly(femur_CA) # Interactive plot 

```

```{r}

Ix_femur <- SMA_fun2(femur, femur$Ix)

plot(Ix_femur, method = "SMA") # SMA plot

femur_Ix <- SMA_plots2(femur, femur$Ix, -3.832083,	0.8201655) #Code for an interactive plot

ggplotly(femur_Ix) # Interactive plot 

```

```{r}
Iy_femur <- SMA_fun2(femur, femur$Iy)

plot(Iy_femur, method = "SMA") # SMA plot

femur_Iy <- SMA_plots2(femur, femur$Iy, -4.489853,	0.8731532) #Code for an interactive plot 

ggplotly(femur_Iy) # Interactive plot 

```

```{r}
J_femur <- SMA_fun2(femur, femur$J)

plot(J_femur, method = "SMA") # SMA plot

femur_J <- SMA_plots2(femur, femur$J, -3.427358,	0.8432931) #Code for an interactive plot

ggplotly(femur_J) # Interactive plot 

```

```{r}
Zx_femur <- SMA_fun1(femur, femur$Zx)

plot(Zx_femur, method = "SMA") # SMA plot

femur_Zx <- SMA_plots1(femur, femur$Zx, -1.120065,	0.7987787) #Code for an interactive plot

ggplotly(femur_Zx) # Interactive plot 
```

```{r}
Zy_femur <- SMA_fun1(femur, femur$Zy)

plot(Zy_femur, method = "SMA") # SMA plot

femur_Zy <- SMA_plots1(femur, femur$Zy, -1.353157,	0.8327825) #Code for an interactive plot

ggplotly(femur_Zy) # Interactive plot 
```

```{r}
Zp_femur <- SMA_fun1(femur, femur$Zp)

plot(Zp_femur, method = "SMA") # SMA plot

femur_Zp <- SMA_plots1(femur, femur$Zp, -0.5153510,	0.8082114	) #Code for an interactive plot

ggplotly(femur_Zp) # Interactive plot 
```

```{r}
P.CA_femur <- P.CA_SMA(femur)  

plot(P.CA_femur, method = "SMA") # SMA plot

femur_P.CA <- P.CA_plot(femur, 54.35371,	0.93848255) #Code for an interactive plot

ggplotly(femur_P.CA) # Interactive plot 

```

#General notes for the femur: 

#tibia 
#Added a correction factor (CF) for the x-ray tibia (CF was determine with a n of 9, ages 3.31-14.05, essentially the yongest to the second oldest in the microCT tibia sample (oldest is 14.59))

#CF was determine by: microCT measurement(s)/x-ray measurement(s) for the bones we had both microCT and x-ray images for, and than we took the mean of those results and applied them to the individuals where we have x-ray images only 
```{r}
TA_tibia <- SMA_fun(tibia, tibia$TA)

plot(TA_tibia, method = "SMA") # SMA plot

tibia_TA <- SMA_plots(tibia, tibia$TA, 2.764478,	0.8195629	) #Code for an interactive plot 

ggplotly(tibia_TA) # Interactive plot 

```

```{r}
MA_tibia <- SMA_fun(tibia, tibia$MA)

plot(MA_tibia, method = "SMA") # SMA plot

tibia_MA <- SMA_plots(tibia, tibia$MA, 1.623709,	0.8823448) #Code for an interactive plot 

ggplotly(tibia_MA) # Interactive plot 

```

```{r}
CA_tibia <- SMA_fun(tibia, tibia$CA)

plot(CA_tibia, method = "SMA") # SMA plot

tibia_CA <- SMA_plots(tibia, tibia$CA, 2.323170,	0.8083081) #Code for an interactive plot 

ggplotly(tibia_CA) # Interactive plot 

```

```{r}

Ix_tibia <- SMA_fun2(tibia, tibia$Ix)

plot(Ix_tibia, method = "SMA") # SMA plot

tibia_Ix <- SMA_plots2(tibia, tibia$Ix, -5.559490,	0.9375193) #Code for an interactive plot

ggplotly(tibia_Ix) # Interactive plot 

#ABRP.042 (x-ray) has two crack with some very minor separation running up the length of the tibia (can be clearly seen internally)

```


```{r}
Iy_tibia <- SMA_fun2(tibia, tibia$Iy)

plot(Iy_tibia, method = "SMA") # SMA plot

tibia_Iy <- SMA_plots2(tibia, tibia$Iy, -3.477810,	0.8218471) #Code for an interactive plot 

ggplotly(tibia_Iy) # Interactive plot 

# Could ABRP.040 be popping out b/c of her age (19.1), or any of our environmental factors (maybe not rank as she is pretty high rank but experienced low rainfall conditions during gestation and moderate rainfall during the first year of life)?

# ABRP.035 is similar to ABRP.018, in that one section of the cortical bone is very thick, but I don't see any injury like with ABRP.018 tibia. However, ABRP.035 is very large bodied (estimated body mass 27.8 kg...he is the heaviest/largest in our sample). He also had some other issues going on with him (massive amount of pathology on the right side of his cranial facial bones, maybe an infection or tumors?)

# ABRP.042 (x-ray) has two crack with some very minor separation running up the length of the tibia (can be clearly seen internally)

# I mention the environmental conditions b/c based on our results with the long bone measurements, and previous studies in humans, the tibia seems to be more sensitive to external environment 
```

```{r}
J_tibia <- SMA_fun2(tibia, tibia$J)

plot(J_tibia, method = "SMA") # SMA plot

tibia_J <- SMA_plots2(tibia, tibia$J, -4.053336,	0.9001997) #Code for an interactive plot

ggplotly(tibia_J) # Interactive plot 

```

```{r}
Zx_tibia <- SMA_fun1(tibia, tibia$Zx)

plot(Zx_tibia, method = "SMA") # SMA plot

tibia_Zx <- SMA_plots1(tibia, tibia$Zx, -2.076552,	0.8964498) #Code for an interactive plot

ggplotly(tibia_Zx) # Interactive plot 
```

```{r}
Zy_tibia <- SMA_fun1(tibia, tibia$Zy)

plot(Zy_tibia, method = "SMA") # SMA plot

tibia_Zy <- SMA_plots1(tibia, tibia$Zy, -1.252525,	0.8346947) #Code for an interactive plot

ggplotly(tibia_Zy) # Interactive plot 
```

```{r}
Zp_tibia <- SMA_fun1(tibia, tibia$Zp)

plot(Zp_tibia, method = "SMA") # SMA plot

tibia_Zp <- SMA_plots1(tibia, tibia$Zp, -1.153346,	0.8737902) #Code for an interactive plot

ggplotly(tibia_Zp) # Interactive plot 
```

```{r}
P.CA_tibia <- P.CA_SMA(tibia) 

plot(P.CA_tibia, method = "SMA") # SMA plot

tibia_P.CA <- P.CA_plot(tibia, 71.00426,	-0.8212398) #Code for an interactive plot

ggplotly(tibia_P.CA) # Interactive plot 

```

#General notes about the tibia: I think the CF makes the x-ray images fit better with the microCT.


#radius - just to see, however, the radius shape is very triangluar 
```{r}
TA_radius <- SMA_fun(radius, radius$TA)

plot(TA_radius, method = "SMA") # SMA plot

radius_TA <- SMA_plots(radius, radius$TA, 2.192758,	0.7855019) #Code for an interactive plot 

ggplotly(radius_TA) # Interactive plot 

```

```{r}
MA_radius <- SMA_fun(radius, radius$MA)

plot(MA_radius, method = "SMA") # SMA plot

radius_MA <- SMA_plots(radius, radius$MA, 1.036426,	0.8059092) #Code for an interactive plot

ggplotly(radius_MA) # Interactive plot 

```

```{r}
CA_radius <- SMA_fun(radius, radius$CA)

plot(CA_radius, method = "SMA") # SMA plot

radius_CA <- SMA_plots(radius, radius$CA, 1.774358,	0.7876877	) #Code for an interactive plot 

ggplotly(radius_CA) # Interactive plot 

```

```{r}

Ix_radius <- SMA_fun2(radius, radius$Ix)

plot(Ix_radius, method = "SMA") # SMA plot

radius_Ix <- SMA_plots2(radius, radius$Ix, -6.021332,	0.8744431) #Code for an interactive plot

ggplotly(radius_Ix) # Interactive plot 

```


```{r}
Iy_radius <- SMA_fun2(radius, radius$Iy)

plot(Iy_radius, method = "SMA") # SMA plot

radius_Iy <- SMA_plots2(radius, radius$Iy, -5.686578,	0.8885873) #Code for an interactive plot 

ggplotly(radius_Iy) # Interactive plot 

```

```{r}
J_radius <- SMA_fun2(radius, radius$J)

plot(J_radius, method = "SMA") # SMA plot

radius_J <- SMA_plots2(radius, radius$J, -5.018385,	0.8711712	) #Code for an interactive plot

ggplotly(radius_J) # Interactive plot 

```

```{r}
Zx_radius <- SMA_fun1(radius, radius$Zx)

plot(Zx_radius, method = "SMA") # SMA plot

radius_Zx <- SMA_plots1(radius, radius$Zx, -2.728911,	0.8705826	) #Code for an interactive plot

ggplotly(radius_Zx) # Interactive plot 

#ABRP.040 (x-ray image), measurement and numbers correct, however, radius was very pathological on the distal end (photographed) and from the x-ray image you can see the cortical bone is super think on one side (possible due to the severe pathology). 
```

```{r}
Zy_radius <- SMA_fun1(radius, radius$Zy)

plot(Zy_radius, method = "SMA") # SMA plot

radius_Zy <- SMA_plots1(radius, radius$Zy, -2.543691,	0.8855411) #Code for an interactive plot

ggplotly(radius_Zy) # Interactive plot 

#ABRP.040 (x-ray image), measurement and numbers correct, however, radius was very pathological on the distal end (photographed) and from the x-ray image you can see the cortical bone is super think on one side (possible due to the severe pathology). 
```

```{r}
Zp_radius <- SMA_fun1(radius, radius$Zp)

plot(Zp_radius, method = "SMA") # SMA plot

radius_Zp <- SMA_plots1(radius, radius$Zp, -1.885296,	0.8637240) #Code for an interactive plot

ggplotly(radius_Zp) # Interactive plot 

#ABRP.040 (x-ray image), measurement and numbers correct, however, radius was very pathological on the distal end (photographed) and from the x-ray image you can see the cortical bone is super think on one side (possible due to the severe pathology).  
```

```{r}
P.CA_radius <- P.CA_SMA(radius)

plot(P.CA_radius, method = "SMA") # SMA plot

radius_P.CA <- P.CA_plot(radius, 75.17294,	-0.90190634) #Code for an interactive plot

ggplotly(radius_P.CA) # Interactive plot 

```


#General notes for the radius: Nothing looks too bad, that being said I don't know if I can judge corretly when something doesn't look right. ***BUT from my understanding the EEM assumes circularity, the radius midshaft are not circular in anyway shape or form. 


